Make any stupid plot you want

### 2021-04-22 draft/sections/implementation.tex
fixed code

\begin{minted}{python}
@dataclass
class FiberBundle:
    K: dict #{'tables': []}
    F: dict #  {variable name: type}
\end{minted}
that asks the user to specify the the properties of \dfiber\ and the \dbase\ connectivity as either discrete vertices or continuous data along edges. To generate the scatter plot and the line plot, the distinction is in the \mintinline{python}{tau} method that is the section. 
\begin{minted}{python}
class PointData:     
    def __init__(self):
      FB = FiberBundle({'tables': ['vertex']},  
                       {'v1': float, 'v2': str, 'v3': float})
    def tau(self, k):
      return # tau evaluated at one point k

class LineData:
  def __init__(self):
    FB = FiberBundle({'tables': ['edge']},  
                     {'x': float, 'y': float, 'color': str})
  def tau(self, k):
    return # tau evaluated on interval k
\end{minted}
The discrete \mintinline{python}{tau} method returns a record of discrete points, akin to a row in a table, while the line\mintinline{python}{tau} returns a sampling of points along an edge \dbasepoint.
\begin{minted}{python}
  def view(self, axes):
      table = defaultdict(list)
      for k in self.keys:
          table['index'].append(k)
          for (name, value) in zip(self.FB.fiber.keys(), 
                                   self.tau(k)[1]):
              table[name].append(value)
      return table
\end{minted}
In both cases, the \mintinline{python}{view} method packages the data into a data structure that the artist can unpack via data component name, akin to a table with column names when \dbase\ is 0 or 1 D.

>>>>

\begin{minted}{python}
@dataclass
class FiberBundle:
    K: dict #{'tables': []}
    F: dict #  {variable name: type}
\end{minted}
that asks the user to specify the the properties of \dfiber\ and the \dbase\ connectivity as either discrete vertices or continuous data along edges. To generate the scatter plot and the line plot, the distinction is in the \mintinline{python}{tau} method that is the section. 
\begin{minted}{python}
class PointData:     
    def __init__(self):
        self.FB = FiberBundle({'tables': ['vertex']},  
                       {'v1': float, 'v2': str, 'v3': float})
    def tau(self, k):
        return # tau evaluated at one point k

class LineData:
    def __init__(self):
        self.FB = FiberBundle({'tables': ['edge']},  
                     {'x': float, 'y': float, 'color': str})
    def tau(self, k):
        return # tau evaluated on interval k
\end{minted}
The discrete \mintinline{python}{tau} method returns a record of discrete points, akin to a row in a table, while the line\mintinline{python}{tau} returns a sampling of points along an edge \dbasepoint.
\begin{minted}{python}
  def view(self, axes):
      table = defaultdict(list)
      for k in self.keys:
          table['index'].append(k)
          for (name, value) in zip(self.FB.fiber.keys(), 
                                   self.tau(k)[1]):
              table[name].append(value)
      return table
\end{minted}
In both cases, the \mintinline{python}{view} method packages the data into a data structure that the artist can unpack via data component name, akin to a table with column names when \dbase\ is 0 or 1 D.
